A Sound and Complete Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2025-08-20 paper/COLA/paper.tex
s/isomorphism/correspondence/

Coq is a proof assistant based on the calculus of inductive
constructions ~\cite{manual_cic}, a higher-order dependently typed
$\lambda$-calculus extended with inductive definitions.  Theorem
proving in Coq follows the ideas of the so-called
``BHK-in\-ter\-pre\-ta\-tion''\footnote{Abbreviation of Brouwer, Heyting,
  Kolmogorov, de Bruijn and Martin-L\"of Correspondence. This is also
  known as the Curry-Howard isomorphism.}, where types represent
logical formulas, $\lambda$-terms represent proofs
\cite{Bertot10} and the task of checking if a piece of text is a
proof of a given formula corresponds to checking if the term that
represents the proof has the type corresponding to the given formula.

>>>>

Coq is a proof assistant based on the calculus of inductive
constructions ~\cite{manual_cic}, a higher-order dependently typed
$\lambda$-calculus extended with inductive definitions.  Theorem
proving in Coq follows the ideas of the so-called
``BHK-in\-ter\-pre\-ta\-tion''\footnote{Abbreviation of Brouwer, Heyting,
  Kolmogorov, de Bruijn and Martin-L\"of correspondence. This is also
  known as the Curry-Howard correspondence.}, where types represent
logical formulas, $\lambda$-terms represent proofs
\cite{Bertot10} and the task of checking if a piece of text is a
proof of a given formula corresponds to checking if the term that
represents the proof has the type corresponding to the given formula.
